Analysis of HTTPS Adoption and Third-party Tracking: \\A Swedish Perspective

### 2015-05-04 paper/figures.tex
Tighter axis labels

\nextgroupplot[
	% title=B1(d) Resp./redir. sec. (http-www),
	allDatasetsStackedYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsStackedYbarPart2,
	swedenHttpWwwDatasetsYbar,
	width=.55\textwidth,
	xticklabels={Counties,Domain registrars,Financial services,GOCS,Higher education,ISPs,Media,Municipalities,Public authorities,reach50,Top 10k .se,Rand 100k .se,},
	xticklabel style={
		rotate=45,
		anchor={north east},
	},
]

@@

\nextgroupplot[
	% title=B2(d) Resp./redir. sec. (http-www),
	allDatasetsStackedYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsStackedYbarPart2,
	globalHttpWwwDatasetsYbar,
	width=.4\textwidth,
	yticklabels={},
	xticklabels={Top 10k .se,Top 10k .dk,Top 10k global,Rand 100k .se,Rand 10k .dk,Rand 10k .com,Rand 10k .net,Rand 10k global,},
	xticklabel style={
		rotate=45,
		anchor={north east},
	},
]

@@

\tikzsetnextfilename{mini-1x1-internal-resources-cdf}
\begin{tikzpicture}
\begin{axis}[
	% title=(a) Internal resources,
	datasetsCDF,
	datasetsCDFMiniResults,
	xlabel=Ratio of internal resources,
	ylabel=Ratio of domains,
	legend style={at={(1.025,.5)}, anchor=west},
]

>>>>

\nextgroupplot[
	% title=B1(d) Resp./redir. sec. (http-www),
	allDatasetsStackedYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsStackedYbarPart2,
	swedenHttpWwwDatasetsYbar,
	paperTight,
	width=.55\textwidth,
	xticklabels={Counties,Domain registrars,Financial services,GOCS,Higher education,ISPs,Media,Municipalities,Public authorities,reach50,Top 10k .se,Rand 100k .se,},
	xticklabel style={
		rotate=45,
		anchor={north east},
	},
]

@@

\nextgroupplot[
	% title=B2(d) Resp./redir. sec. (http-www),
	allDatasetsStackedYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsStackedYbarPart2,
	globalHttpWwwDatasetsYbar,
	paperTight,
	width=.4\textwidth,
	yticklabels={},
	xticklabels={Top 10k .se,Top 10k .dk,Top 10k global,Rand 100k .se,Rand 10k .dk,Rand 10k .com,Rand 10k .net,Rand 10k global,},
	xticklabel style={
		rotate=45,
		anchor={north east},
	},
]

@@

\tikzsetnextfilename{mini-1x1-internal-resources-cdf}
\begin{tikzpicture}
\begin{axis}[
	% title=(a) Internal resources,
	datasetsCDF,
	datasetsCDFMiniResults,
	paperTight,
	xlabel=Ratio of internal resources,
	ylabel=Ratio of domains,
	legend style={at={(1.03,.5)}, anchor=west},
	xlabel style={
		at={(0.5,0.1)}
	},
	ylabel style={
		at={(0.17,0.5)}
	},
]
